研究者の卵のいろは

### 2023-07-03 index.Rmd
2307031230

--- 
title: "研究者の卵に向けたささやかな囁き"
author: "tabutan"
date: "`r Sys.Date()`"
output: 
  bookdown::gitbook:
    split_bib: yes  
    number_sections: true   
    toc_depth: 4 
    css: custom_style.css   
site: bookdown::bookdown_site  
output_dir: "docs"  
documentclass: book  
header-includes:
   - \usepackage{amsmath}
   - \usepackage{nccmath}
bibliography: reference_studymethod.bib   
csl: nature.csl
link-citations: yes
---

>>>>

--- 
title: "研究者の卵のいろは"
author: "tabutan"
date: "`r Sys.Date()`"
output: 
  bookdown::gitbook:
    split_bib: yes  
    number_sections: true   
    toc_depth: 4 
    css: custom_style.css   
site: bookdown::bookdown_site  
output_dir: "docs"  
documentclass: book  
header-includes:
   - \usepackage{amsmath}
   - \usepackage{nccmath}
bibliography: reference_studymethod.bib   
csl: nature.csl
link-citations: yes
---
